---
title: "Asset Mix Strategy"
author: "Quant Team"
date: "Feb 21, 2017"
output:
  ioslides_presentation:
    css: vestcor_style.css
    logo: vestcor_logo.png
    toc: yes
  beamer_presentation: default
---
# Momentum Model Update

## Summary

Current Posn: 20bps Canada, 20bps U.S., 20bps EAFE, 10bps EM, 0bps REITs

-  Canada above both 100D & 200D SMA (Full Position Implied)
-  U.S. above both 100D & 200D SMA (Full Position Implied)
-  EAFE above both 100D & 200D SMA (Full Position Implied)
-  EM above both (Full Position Implied)
-  U.S. REITs is above 100D SMA and it is slightly higher than 200D SMA (Full Position Implied)


## S&P 500 {#myStyle}

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(quantmod,quietly = TRUE)
library(Rbbg,quietly=TRUE)
library(xts,quietly=TRUE)
con = blpConnect(verbose = FALSE)
analysis.date = Sys.Date()
start.date = as.Date("1998-12-31")
symbols = c("SPX Index")
hist = bdh(con,symbols,"px_last",start.date,analysis.date)
hist.xts = xts(hist[,2],order.by=as.Date(hist[,1]))
hist.xts = na.locf(hist.xts)
hist.xts = na.locf(hist.xts,fromLast=TRUE)
spx = hist.xts[,1]
colnames(spx) = "Close"
chart_Series(spx,TA='add_SMA(200);add_SMA(100,col="blue")',name="S&P 500 Index")
blpDisconnect(con)
```

## TSX Composite {#myStyle}

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(quantmod,quietly = TRUE)
library(Rbbg,quietly=TRUE)
library(xts,quietly=TRUE)
con = blpConnect(verbose = FALSE)
analysis.date = Sys.Date()
start.date = as.Date("1998-12-31")
symbols = c("SPTSX Index")
hist = bdh(con,symbols,"px_last",start.date,analysis.date)
hist.xts = xts(hist[,2],order.by=as.Date(hist[,1]))
hist.xts = na.locf(hist.xts)
hist.xts = na.locf(hist.xts,fromLast=TRUE)
spx = hist.xts[,1]
colnames(spx) = "Close"
chart_Series(spx,TA='add_SMA(200);add_SMA(100,col="blue")',name="TSX Composite Index")
```


## MSCI EAFE {#myStyle}

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(quantmod,quietly = TRUE)
library(Rbbg,quietly=TRUE)
library(xts,quietly=TRUE)
con = blpConnect(verbose = FALSE)
analysis.date = Sys.Date()
start.date = as.Date("1998-12-31")
symbols = c("MXEA Index")
hist = bdh(con,symbols,"px_last",start.date,analysis.date)
hist.xts = xts(hist[,2],order.by=as.Date(hist[,1]))
hist.xts = na.locf(hist.xts)
hist.xts = na.locf(hist.xts,fromLast=TRUE)
spx = hist.xts[,1]
colnames(spx) = "Close"
chart_Series(spx,TA='add_SMA(200);add_SMA(100,col="blue")',name="MSCI EAFE Index")
```


## MSCI Emerging Markets {#myStyle}

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(quantmod,quietly = TRUE)
library(Rbbg,quietly=TRUE)
library(xts,quietly=TRUE)
con = blpConnect(verbose = FALSE)
analysis.date = Sys.Date()
start.date = as.Date("1998-12-31")
symbols = c("MXEF Index")
hist = bdh(con,symbols,"px_last",start.date,analysis.date)
hist.xts = xts(hist[,2],order.by=as.Date(hist[,1]))
hist.xts = na.locf(hist.xts)
hist.xts = na.locf(hist.xts,fromLast=TRUE)
spx = hist.xts[,1]
colnames(spx) = "Close"
chart_Series(spx,TA='add_SMA(200);add_SMA(100,col="blue")',name="MSCI EM Index")
```

## US Equity REITs {#myStyle}

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(quantmod,quietly = TRUE)
library(Rbbg,quietly=TRUE)
library(xts,quietly=TRUE)
con = blpConnect(verbose = FALSE)
analysis.date = Sys.Date()
start.date = as.Date("1998-12-31")
symbols = c("FNER Index")
hist = bdh(con,symbols,"px_last",start.date,analysis.date)
hist.xts = xts(hist[,2],order.by=as.Date(hist[,1]))
hist.xts = na.locf(hist.xts)
hist.xts = na.locf(hist.xts,fromLast=TRUE)
spx = hist.xts[,1]
colnames(spx) = "Close"
chart_Series(spx,TA='add_SMA(200);add_SMA(100,col="blue")',name="FTSE US Equity REIT Index")
```

